---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r}
#| include: false
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
options(str = strOptions(strict.width = "cut"))
```

# bbk

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/m-muecke/bbk/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/m-muecke/bbk/actions/workflows/R-CMD-check.yaml)
[![CRAN status](https://www.r-pkg.org/badges/version/bbk)](https://CRAN.R-project.org/package=bbk)
[![R-universe version](https://m-muecke.r-universe.dev/bbk/badges/version)](https://m-muecke.r-universe.dev/bbk)
<!-- badges: end -->

bbk is minimal R client for the following APIs:

- [Banco de España (BdE)](https://www.bde.es/webbe/en/estadisticas/recursos/api-estadisticas-bde.html)
- [Bank of England (BoE)](https://www.bankofengland.co.uk/boeapps/database)
- [Banque de France (BdF)](https://webstat.banque-france.fr/en/pages/guide-migration-api/)
- [Deutsche Bundesbank (BBk)](https://www.bundesbank.de/en/statistics/time-series-databases/help-for-sdmx-web-service)
- [European Central Bank (ECB)](https://data.ecb.europa.eu/help/api/overview)
- [Swiss National Bank (SNB)](https://data.snb.ch/en)
- [Österreichische Nationalbank (OeNB)](https://www.oenb.at/en/Statistics/User-Defined-Tables/webservice.html)

> In the future, it may be extended to other central banks and financial institutions.
> Feel free to open an issue if you have a specific request.

## Installation

You can install the released version of bbk from [CRAN](https://CRAN.R-project.org) with:

```{r}
#| eval: false
install.packages("bbk")
```

And the development version from [GitHub](https://github.com/) with:

```{r}
#| eval: false
# install.packages("pak")
pak::pak("m-muecke/bbk")
```

## Usage

bbk functions are prefixed according to the central bank they access (`bbk_`, `ecb_`, `snb_`,
`boe_`, `bde_`, `bdf_`, `onb_`) and follow the naming conventions of their respective APIs.

The typical workflow involves:

1. Finding the time series identifier on the relevant central bank's website
2. Using the appropriate bbk function to retrieve the data

```{r}
#| label: demo
#| message: false
library(bbk)

# Deutsche Bundesbank - fetch 10 year daily yield curve
yield_curve <- bbk_data(
  flow = "BBSIS",
  key = "D.I.ZAR.ZI.EUR.S1311.B.A604.R10XX.R.A.A._Z._Z.A",
  start_period = "2020-01-01"
)
```

```{r}
#| label: plotting
#| message: false
#| echo: false
#| dpi: 300
library(ggplot2)

ggplot(yield_curve, aes(x = date, y = value)) +
  geom_line() +
  theme_minimal() +
  theme(
    plot.title = element_text(face = "bold"),
    panel.grid.major.y = element_line(color = "black", linewidth = 0.2),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text = element_text(color = "black"),
    axis.title = element_blank()
  ) +
  scale_y_continuous(labels = scales::label_percent(scale = 1L)) +
  labs(title = "Daily Yields of 10-Year Federal Securities")
```

## Related work

* [SNBdata](https://github.com/enricoschumann/SNBdata): R package for downloading data from the Swiss National Bank (SNB).
* [bundesbank](https://github.com/enricoschumann/bundesbank): R scripts for downloading time-series data from the Bundesbank.
* [ecb](https://github.com/expersso/ecb): R interface to the European Central Bank's Statistical Data Warehouse (SDW) API.
* [oenb](https://github.com/franzmohr/oenb): R package for accessing the OeNB's API.
* [pdfetch](https://github.com/abielr/pdfetch): R package for downloading economic and financial time series from public sources.
* [readsdmx](https://github.com/mdequeljoe/readsdmx): R package for reading SDMX data and metadata.
* [rsdmx](https://github.com/opensdmx/rsdmx): R package for reading SDMX data and metadata.
* [tidyBdE](https://github.com/rOpenSpain/tidyBdE): R package for accessing the Banco de España's API.
