---
title: "Getting started with bbk"
---

```{r}
#| include: false
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

bbk gives you one consistent way to pull data from many central bank APIs.
Every workflow follows the same two steps, no matter which bank you query:

1. **Find the identifier** of the series (or dataset) you want.
2. **Fetch it** with the matching `*_data()` function.

```{r}
#| message: false
library(bbk)
```

## Step 1: find the identifier

Most central banks organise data into *datasets* (dataflows), each built on a *data structure* that
defines the dimensions whose codes combine into a series key. bbk lets you explore both from R.

Browse the Bundesbank's available dataflows:

```{r}
head(bbk_metadata("dataflow"))
```

Take `BBEX3`, the exchange-rate dataset. It is built on the `BBK_ERX` data structure, whose
dimensions you can list with `bbk_dimension()`:

```{r}
bbk_dimension("BBK_ERX")
```

Each dimension supplies one dot-separated part of the key. So a monthly (`M`) US dollar (`USD`) per
euro (`EUR`) rate, of series type `BB`, rate type `AC`, suffix `A01`, has the key
`M.USD.EUR.BB.AC.A01`.

## Step 2: fetch the data

Pass the dataflow and key to `bbk_data()`:

```{r}
usd_eur = bbk_data("BBEX3", key = "M.USD.EUR.BB.AC.A01", start_period = "2015-01-01")
head(usd_eur)
```

Every `*_data()` function returns a tidy `data.table` with a `date` column and a `value` column,
ready for analysis or plotting.

The same two steps work for every supported bank: swap the prefix (`bbk_`, `ecb_`, `snb_`, `cnb_`,
...) and use that bank's discovery and `*_data()` functions. See the
[function reference](../reference/index.html) for what each bank provides, and
[Comparing exchange rates across central banks](cross-bank-comparison.html) for a worked example
that pulls a comparable series from several banks at once.

## Caching

bbk can cache API responses on disk, so re-running a query is instant and you avoid hammering the
upstream API. Caching is **off by default**; enabling it is recommended:

```{r}
#| eval: false
options(bbk.cache = TRUE)
```

Put that line in your `.Rprofile` to enable caching for every session. Cached responses are kept
for one day by default; tune this with `options(bbk.cache_max_age = <seconds>)`. Inspect or clear
the cache with:

```{r}
#| eval: false
bbk_cache_dir()    # where responses are stored
bbk_cache_clear()  # wipe the cache
```

## Where to go next

- The function reference, grouped by bank, lists every available endpoint.
- Each `*_data()` help page documents that bank's identifier scheme and links to its official
  catalogue.
